---
title: "Cookie Sales"
output: 
  flexdashboard::flex_dashboard:
    source_code: embed
    navbar:
        - { icon: "fa-github", href: "https://github.com/ModelBehavior", align: right}
        - { icon: "fa-linkedin", href: "https://www.linkedin.com/in/rashawn-howard/", align: right}
    theme:
      bootswatch: united
  
---

```{r setup, include=FALSE}
library(tidyverse)
library(crosstalk)
library(htmlwidgets)
library(highcharter)
library(flexdashboard)

knitr::opts_chunk$set(echo = FALSE)

sales <- readxl::read_excel("/Users/rashawnhoward/Downloads/EXCEL/Cookie_Sales.xlsx", sheet = "Data")

sales <- sales %>% janitor::clean_names()
head(sales)

sales_product_lvl <- levels(sales$product)

shared_sales_data <- SharedData$new(sales)
```

Dashboard {data-icon="fa-home"}
===================================== 

## Row 1

### Total Profit
```{r}
sales %>% 
  summarise(profit = round(sum(profit))) %>% 
  valueBox(caption = "Total Profit", icon = "fa-thumbs-up", 
           color = "lightgreen")
```

### Total Units Sold
```{r}
sales %>% 
  summarise(units_sold = sum(units_sold)) %>% 
  valueBox(caption = "Total Units Sold", 
           icon = "fa-truck",
           color = "lightblue")
```

### Average Units Sold by Country
```{r}
sales %>% 
   group_by(country) %>% 
   summarise(units_sold = round(mean(units_sold))) %>% 
   hchart("pie", hcaes(x = country, y = units_sold),
          name = "Average Units Sold") %>% 
  hc_exporting(
    enabled = TRUE, filename="pie_graph2")
```

### Average Profit by Country
```{r}
 sales %>% 
   group_by(country) %>% 
   summarise(profit = round(mean(profit))) %>% 
   hchart("pie", hcaes(x = country, y = profit),
         name = "Average Profit") %>% 
  hc_exporting(
    enabled = TRUE, filename="pie_graph1")
```

## Column 1

### Profit by Month

```{r}
sales %>% 
  mutate(month = lubridate::month(date)) %>% 
  group_by(month) %>% 
  summarise(profit = sum(profit)) %>% 
  hchart(type = "line", hcaes(x  = month, y = profit),
         name =  "Profit") %>% 
  hc_exporting(
    enabled = TRUE, filename="line_graph1")
```

### Units Sold by Month

```{r}
sales %>% 
  mutate(month = lubridate::month(date)) %>% 
  group_by(month) %>% 
  summarise(units_sold = sum(units_sold)) %>% 
  hchart(type  = "line", hcaes(x = month, y = units_sold),
         name = "Units Sold") %>% 
  hc_exporting(
    enabled = TRUE, filename="line_graph2")
```

## Column 2

### Profit by Market and Cookie Type

```{r}
sales %>% 
  group_by(country,product) %>% 
  summarise(profit = sum(profit)) %>% 
  highcharter::hchart(type = "bar", hcaes(x = country, y = profit, 
                                          group = product)) %>% 
  hc_exporting(
    enabled = TRUE, filename="bar_graph")
```

Data {data-icon="fa-table"}
===================================== 
```{r}
sales %>% 
  mutate(date = lubridate::ymd(date)) %>% 
  DT::datatable( extensions = 'Buttons',  filter = 'top', options = list(searchHighlight = TRUE, pageLength = 15, dom = 'Bfrtip',
                                                                                                 buttons = 
                                                 list( list(
                                                   extend = 'collection',
                                                  buttons = list(list(extend='csv',filename='cookie_sales.csv'),
                                                                 list(extend='excel',
                                                                      filename = 'cookie_sales.xlsx') ),text="Download"
                                                               
                                                                                                 
))))

